Practical Optional Types for Clojure

### 2016-01-07 formal-model.tex
explain hmap lookups

An absent lookup is checked by T-GetHMapAbsent.
$$
\abs{\makelocal{b}}{\Breakfast}{\getexp{\makelocal{b}}{\makekw{bocce}}}
$$
The result type is \Nil, and the return object is \path{\keype{\makekw{bocce}}}{\makelocal{b}}.

A lookup that is not present or absent is checked by
T-GetHMapPartialDefault.
$$
\abs{\makelocal{u}}{\Lunch}{\getexp{\makelocal{u}}{\makekw{bocce}}}
$$
The result type is \Top, and the return object is \path{\keype{\makekw{bocce}}}{\makelocal{u}}.
Notice propositions are erased once they enter a HMap type.

>>>>

An absent lookup is checked by T-GetHMapAbsent.
$$
\abs{\makelocal{b}}{\Breakfast}{\getexp{\makelocal{b}}{\makekw{bocce}}}
$$
The result type is \Nil---since \Breakfast is fully specified---with return object \path{\keype{\makekw{bocce}}}{\makelocal{b}}.

A lookup that is not present or absent is checked by
T-GetHMapPartialDefault.
$$
\abs{\makelocal{u}}{\Lunch}{\getexp{\makelocal{u}}{\makekw{bocce}}}
$$
The result type is \Top---since {\Lunch} has an unknown \makekw{bocce} entry---with return object \path{\keype{\makekw{bocce}}}{\makelocal{u}}.
Notice propositions are erased once they enter a HMap type.
